High-Order Accurate Finite Difference Schemes \\ Via Optimal Time Step Selection

### 2008-06-09 papers/OTSPDE/OTSPDE.tex
OTSPDE: * changed color scheme in figures so that the graphs show up better in   greyscale * minor changes to keywords and short title in manuscript * added submission information directory

\begin{keywords}
optimal time step, finite difference methods, high-order accurate numerical 
methods, time dependent PDEs
\end{keywords}

@@

\pagestyle{myheadings}
\thispagestyle{plain}
\markboth{KEVIN T. CHU}
         {HIGH-ORDER FD SCHEMES VIA OPTIMAL TIME STEP SELECTION}

>>>>

\begin{keywords}
optimal time step, finite difference schemes, high-order accurate numerical 
methods, time dependent PDEs
\end{keywords}

@@

\pagestyle{myheadings}
\thispagestyle{plain}
\markboth{KEVIN T. CHU}
         {HIGH-ORDER FD SCHEMES VIA OPTIMAL TIME STEPS}
